On the performance of the MAC model

### 2018-11-02 2018_nips_vigil/smac.tex

\subsection{Simplified MAC network}
Our proposed modification to the MAC network is based on two heuristic
simplifications of the MAC cell. 
First, we observe that, taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
Next, we assume that dimension-preserving linear layers are invertible
so as to avoid information loss. 
Applying this principle to the equations, with a careful reorganization,
we can apply a single linear layer to the knowledge base \emph{prior}
to all the reasoning steps and work with this \emph{projected} knowledge base
as-is throughout the reasoning steps.

@@

As seen above, being noticeably simpler, the S-MAC obtains significant reduction in the number of position-independent parameters across all units (see~\tableref{tab:parameters}).
Our experiments demonstrate that this gives us noticeable savings in the training time. However, since the computation time is also dominated by the position-aware layers in the control unit, as well as the input unit, the speedup is not as large as we desire.

>>>>

\subsection{Simplified MAC network}
Our proposed modification to the MAC network is based on two heuristic
simplifications of the MAC cell. 
First, we observe that taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
Next, we assume that dimension-preserving linear layers are invertible
so as to avoid information loss. 
Applying this principle to the equations, with a careful reorganization,
we can apply a single linear layer to the knowledge base \emph{prior}
to all the reasoning steps and work with this \emph{projected} knowledge base
as-is throughout the reasoning steps.

@@

As seen above, being noticeably simpler, the S-MAC obtains significant reduction in the number of position-independent parameters across all units (see~\tableref{tab:parameters}).
Our experiments demonstrate that this gives us noticeable savings in the training time. However, since the computation time is also dominated by the position-aware layers in the Control Unit as well as the input unit so the speedup is not as large as we desire.
